---
title: "SEs&means_amt_acquired_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(readxl)
library(cowplot)
library(forcats)
library(car)
library(Hmisc)
library(multcomp)
stat_sum_df <- function(fun, geom="crossbar", ...) {
  stat_summary(fun.data=fun, colour="red", geom=geom, width=0.2, ...)
}
```

library(nlme)
lme( prot ~ LineType(Line) + diet + Linetype * diet, random=~1|Line, data= all_prot)

#ANOVA
```{r}
new_datdat<-read.table("../processed_data/carbs_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)


dat<-read.table("../processed_data/carbs_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dat$BoxTreat[dat$BoxTreat=="1DS.1"] <- "1DA.1"

dat<-slice(dat,1:37)

test<-dat %>% separate(BoxTreat, c("Line", "Rep"))
test$LineType<-gsub("[[:digit:]]","",test$Line)#Make Treatment column

test<-cbind(dat$BoxTreat, test)
names(test)[names(test) == "dat$BoxTreat"] <- "RIL"

dat<-test

names(dat)[names(dat) == "c_carb_T"] <- "c_carb"
names(dat)[names(dat) == "dr_carb_T"] <- "dr_carb"
names(dat)[names(dat) == "hs_carb_T"] <- "hs_carb"


c_carb<- dplyr::summarize(group_by(dat,Line),carb=mean(c_carb, na.rm = FALSE))#
c_carb$diet<-c("C")
c_carb$LineType<-gsub("[[:digit:]]","",c_carb$Line)#Make LineType column

dr_carb<- dplyr::summarize(group_by(dat,Line),carb=mean(dr_carb, na.rm = FALSE))#
dr_carb$diet<-c("DR")
dr_carb$LineType<-gsub("[[:digit:]]","",dr_carb$Line)#Make LineType column


hs_carb<- dplyr::summarize(group_by(dat,Line),carb=mean(hs_carb, na.rm = FALSE))#
hs_carb$diet<-c("HS")
hs_carb$LineType<-gsub("[[:digit:]]","",hs_carb$Line)#Make LineType column


carb_<-bind_rows(c_carb, dr_carb)
all_carb<-bind_rows(carb_, hs_carb)



#carbalt<- carbalt %>% mutate(treatment=fct_inorder(carbalt$treatment, ordered=NA))
all_carb<-na.omit(all_carb)
##
library(nlme)
#try_this<-lme(carb ~ LineType + diet + LineType * diet, random=~1|Line, data= all_carb)
##
try_this<-lme(carb ~ LineType * diet, random=~1|Line, data= all_carb)

anova.lme(try_this)

#post hoc testing:
tukeyc <- glht(carblm, linfct = mcp(treatment = "Tukey"))
summary(tukeyc)
plot(tukeyc)

```
#post_hoc <- glht(carblm,mcp(Treatment = c("hs - c == 0", "hs - dr == 0")))
#summary(post_hoc)

```{r}
dat<-read.table("../processed_data/lipid_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dat$BoxTreat[dat$BoxTreat=="1DS.1"] <- "1DA.1"

dat<-slice(dat,1:37)

test<-dat %>% separate(BoxTreat, c("Line", "Rep"))
test$LineType<-gsub("[[:digit:]]","",test$Line)#Make Treatment column

test<-cbind(dat$BoxTreat, test)
names(test)[names(test) == "dat$BoxTreat"] <- "RIL"
dat<-test

names(dat)[names(dat) == "c_lip_T"] <- "c_lip"
names(dat)[names(dat) == "dr_lip_T"] <- "dr_lip"
names(dat)[names(dat) == "hs_lip_T"] <- "hs_lip"

c_lip<- dplyr::summarize(group_by(dat,Line),lip=mean(c_lip, na.rm = FALSE))#
c_lip$diet<-c("C")
c_lip$LineType<-gsub("[[:digit:]]","",c_lip$Line)#Make LineType column

dr_lip<- dplyr::summarize(group_by(dat,Line),lip=mean(dr_lip, na.rm = FALSE))#
dr_lip$diet<-c("DR")
dr_lip$LineType<-gsub("[[:digit:]]","",dr_lip$Line)#Make LineType column

hs_lip<- dplyr::summarize(group_by(dat,Line),lip=mean(hs_lip, na.rm = FALSE))#
hs_lip$diet<-c("HS")
hs_lip$LineType<-gsub("[[:digit:]]","",hs_lip$Line)#Make LineType column

lip_<-bind_rows(c_lip, dr_lip)
all_lip<-bind_rows(lip_, hs_lip)

all_lip<-na.omit(all_lip)
library(nlme)
#try_this<-lme(lip ~ LineType + diet + LineType * diet, random=~1|Line, data= all_lip)
try_this<-lme(lip ~ LineType * diet, random=~1|Line, data= all_lip)
anova.lme(try_this)

#post hoc testing:
tukeyc <- glht(liplm, linfct = mcp(treatment = "Tukey"))
summary(tukeyc)
plot(tukeyc)
```

```{r}
dat<-read.table("../processed_data/prot_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dat$BoxTreat[dat$BoxTreat=="1DS.1"] <- "1DA.1"

dat<-slice(dat,1:37)

test<-dat %>% separate(BoxTreat, c("Line", "Rep"))
test$LineType<-gsub("[[:digit:]]","",test$Line)#Make Treatment column

test<-cbind(dat$BoxTreat, test)
names(test)[names(test) == "dat$BoxTreat"] <- "RIL"
dat<-test

names(dat)[names(dat) == "c_prot_T"] <- "c_prot"
names(dat)[names(dat) == "dr_prot_T"] <- "dr_prot"
names(dat)[names(dat) == "hs_prot_T"] <- "hs_prot"

c_prot<- dplyr::summarize(group_by(dat,Line),prot=mean(c_prot, na.rm = FALSE))#
c_prot$diet<-c("C")
c_prot$LineType<-gsub("[[:digit:]]","",c_prot$Line)#Make LineType column

dr_prot<- dplyr::summarize(group_by(dat,Line),prot=mean(dr_prot, na.rm = FALSE))#
dr_prot$diet<-c("DR")
dr_prot$LineType<-gsub("[[:digit:]]","",dr_prot$Line)#Make LineType column

hs_prot<- dplyr::summarize(group_by(dat,Line),prot=mean(hs_prot, na.rm = FALSE))#
hs_prot$diet<-c("HS")
hs_prot$LineType<-gsub("[[:digit:]]","",hs_prot$Line)#Make LineType column

prot_<-bind_rows(c_prot, dr_prot)
all_prot<-bind_rows(prot_, hs_prot)

all_prot<-na.omit(all_prot)
library(nlme)
#try_this<-lme(prot ~ LineType + diet + LineType * diet, random=~1|Line, data= all_prot)
try_this<-lme(prot ~ LineType * diet, random=~1|Line, data= all_prot)
anova.lme(try_this)

#post hoc testing:
tukeyc <- glht(protlm, linfct = mcp(treatment = "Tukey"))
summary(tukeyc)
plot(tukeyc)
```

```{r}
dat<-read.table("../processed_data/glycogen_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dat$BoxTreat[dat$BoxTreat=="1DS.1"] <- "1DA.1"

dat<-slice(dat,1:37)

test<-dat %>% separate(BoxTreat, c("Line", "Rep"))
test$LineType<-gsub("[[:digit:]]","",test$Line)#Make Treatment column

test<-cbind(dat$BoxTreat, test)
names(test)[names(test) == "dat$BoxTreat"] <- "RIL"
dat<-test

names(dat)[names(dat) == "c_gly_T"] <- "c_gly"
names(dat)[names(dat) == "dr_gly_T"] <- "dr_gly"
names(dat)[names(dat) == "hs_gly_T"] <- "hs_gly"

c_gly<- dplyr::summarize(group_by(dat,Line),gly=mean(c_gly, na.rm = FALSE))#
c_gly$diet<-c("C")
c_gly$LineType<-gsub("[[:digit:]]","",c_gly$Line)#Make LineType column

dr_gly<- dplyr::summarize(group_by(dat,Line),gly=mean(dr_gly, na.rm = FALSE))#
dr_gly$diet<-c("DR")
dr_gly$LineType<-gsub("[[:digit:]]","",dr_gly$Line)#Make LineType column

hs_gly<- dplyr::summarize(group_by(dat,Line),gly=mean(hs_gly, na.rm = FALSE))#
hs_gly$diet<-c("HS")
hs_gly$LineType<-gsub("[[:digit:]]","",hs_gly$Line)#Make LineType column

gly_<-bind_rows(c_gly, dr_gly)
all_gly<-bind_rows(gly_, hs_gly)

all_gly<-na.omit(all_gly)
library(nlme)
#try_this<-lme(gly ~ LineType + diet + LineType * diet, random=~1|Line, data= all_gly)
try_this<-lme(gly ~ LineType * diet, random=~1|Line, data= all_gly)
anova.lme(try_this)

posthoc<-glht(try_this)
summary(posthoc)


#post hoc testing:
#tukeyc <- glht(glylm, linfct = mcp(treatment = "Tukey"))
#summary(tukeyc)
#plot(tukeyc)
```



###OLD ANOVAs
```{r}
dat<-read.table("../processed_data/lipid_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
names(dat)[names(dat) == "BoxTreat"] <- "RIL"
names(dat)[names(dat) == "c_lip_T"] <- "c_lip"
names(dat)[names(dat) == "dr_lip_T"] <- "dr_lip"
names(dat)[names(dat) == "hs_lip_T"] <- "hs_lip"

lipalt<-data.frame('value'=c(dat[,'dr_lip'],dat[,'c_lip'],dat[,'hs_lip']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

lipalt<- lipalt%>% mutate(treatment=fct_inorder(lipalt$treatment, ordered=NA))

liplm<-lm(value~ treatment, data=lipalt)
summary(liplm)
anova(liplm)

tukeyl <- glht(liplm, linfct = mcp(treatment = "Tukey"))
summary(tukeyl)
plot(tukeyl)
```


```{r}
dat<-read.table("../processed_data/prot_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
names(dat)[names(dat) == "BoxTreat"] <- "RIL"
names(dat)[names(dat) == "c_prot_T"] <- "c_prot"
names(dat)[names(dat) == "dr_prot_T"] <- "dr_prot"
names(dat)[names(dat) == "hs_prot_T"] <- "hs_prot"

protalt<-data.frame('value'=c(dat[,'dr_prot'],dat[,'c_prot'],dat[,'hs_prot']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

protalt<- protalt%>% mutate(treatment=fct_inorder(protalt$treatment, ordered=NA))

protlm<-lm(value~ treatment, data=protalt)
summary(protlm)
anova(protlm)
tukeyp <- glht(protlm, linfct = mcp(treatment = "Tukey"))
summary(tukeyp)
plot(tukeyp)
```


```{r}
dat<-read.table("../processed_data/glycogen_transform.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
names(dat)[names(dat) == "BoxTreat"] <- "RIL"
names(dat)[names(dat) == "c_gly_T"] <- "c_gly"
names(dat)[names(dat) == "dr_gly_T"] <- "dr_gly"
names(dat)[names(dat) == "hs_gly_T"] <- "hs_gly"

glyalt<-data.frame('value'=c(dat[,'dr_gly'],dat[,'c_gly'],dat[,'hs_gly']),'treatment'=rep(c('dr','c', 'hs'),each=nrow(dat)), 'RIL'=rep(c(dat[,'RIL'])))

glyalt<- glyalt%>% mutate(treatment=fct_inorder(glyalt$treatment, ordered=NA))

glylm<-lm(value~ treatment, data=glyalt)
summary(glylm)
anova(glylm)

tukeyg<- glht(glylm, linfct = mcp(treatment = "Tukey"))
summary(tukeyg)
plot(tukeyg)
```




















```{r}
#dat<-read.table("../processed_data/all_carb_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

#dat<-read.table("../processed_data/ov_carb_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
#dat<-read.table("../processed_data/bo_carb_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)


#standard error (SE) and means
mean(dat$dr_carb, na.rm=TRUE)
sd(dat$dr_carb, na.rm=TRUE)/sqrt(length(dat$dr_carb[!is.na(dat$dr_carb)]))#Std error

mean(dat$c_carb, na.rm=TRUE)
sd(dat$c_carb, na.rm=TRUE)/sqrt(length(dat$c_carb[!is.na(dat$c_carb)]))  #Standard error

mean(dat$hs_carb, na.rm=TRUE)
sd(dat$hs_carb, na.rm=TRUE)/sqrt(length(dat$hs_carb[!is.na(dat$hs_carb)]))  #Std error

```


```{r}
#dat<-read.table("../processed_data/all_lip_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

#dat<-read.table("../processed_data/ov_lip_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
#dat<-read.table("../processed_data/bo_lip_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)


mean(dat$dr_lip, na.rm=TRUE)
sd(dat$dr_lip, na.rm=TRUE)/sqrt(length(dat$dr_lip[!is.na(dat$dr_lip)]))#Std error

mean(dat$c_lip, na.rm=TRUE)
sd(dat$c_lip, na.rm=TRUE)/sqrt(length(dat$c_lip[!is.na(dat$c_lip)]))  #Standard error

mean(dat$hs_lip, na.rm=TRUE)
sd(dat$hs_lip, na.rm=TRUE)/sqrt(length(dat$hs_lip[!is.na(dat$hs_lip)]))  #Std error
```


```{r}
#dat<-read.table("../processed_data/all_prot_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

#dat<-read.table("../processed_data/ov_prot_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dat<-read.table("../processed_data/bo_prot_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)


mean(dat$dr_prot, na.rm=TRUE)
sd(dat$dr_prot, na.rm=TRUE)/sqrt(length(dat$dr_prot[!is.na(dat$dr_prot)]))#Std error

mean(dat$c_prot, na.rm=TRUE)
sd(dat$c_prot, na.rm=TRUE)/sqrt(length(dat$c_prot[!is.na(dat$c_prot)]))  #Standard error

mean(dat$hs_prot, na.rm=TRUE)
sd(dat$hs_prot, na.rm=TRUE)/sqrt(length(dat$hs_prot[!is.na(dat$hs_prot)]))  #Std error
```

```{r}
#dat<-read.table("../processed_data/all_gly_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

#dat<-read.table("../processed_data/ov_gly_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)
dat<-read.table("../processed_data/bo_gly_tot.txt", sep="\t",header=TRUE,stringsAsFactors=FALSE)

mean(dat$dr_gly, na.rm=TRUE)
sd(dat$dr_gly, na.rm=TRUE)/sqrt(length(dat$dr_gly[!is.na(dat$dr_gly)]))#Std error

mean(dat$c_gly, na.rm=TRUE)
sd(dat$c_gly, na.rm=TRUE)/sqrt(length(dat$c_gly[!is.na(dat$c_gly)]))  #Standard error

mean(dat$hs_gly, na.rm=TRUE)
sd(dat$hs_gly, na.rm=TRUE)/sqrt(length(dat$hs_gly[!is.na(dat$hs_gly)]))  #Std error
```

