---
title: "outlier_removal&plot"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(plyr)
library(forcats)
setwd("C:/Users/Anna/Dropbox/AMP_EGK/Projects/Selection/scripts")

```

#overall dataset (for removal of outliers)
whole_body_combined_process.txt

#outlier list
liplist<-read.table("../processed_data/liplist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
protlist<-read.table("../processed_data/protlist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
carblist<-read.table("../processed_data/carblist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
glylist<-read.table("../processed_data/glylist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

#lipds (there are no outliers)
```{r}
combined<-read.table("../processed_data/whole_body_combined_process.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

liplist<-read.table("../processed_data/liplist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

```

#everybody else 
```{r}
protlist<-read.table("../processed_data/protlist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE) #3DA.C.1
carblist<-read.table("../processed_data/carblist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)#2DA.HS.2
glylist<-read.table("../processed_data/glylist_outliers.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)#2FA.HS.2

combined$p_tot_perfly[combined$p_tot_perfly>0.008927641] <- NA
combined$c_tot_perfly[combined$c_tot_perfly>0.1447852] <- NA
combined$g_tot_perfly[combined$g_tot_perfly>1.53968] <- NA

write.table(combined, "../processed_data/whole_olier_rem.txt", sep="\t")#USE THIS
```
Clear working directory
```{r}
combined<-read.table("../processed_data/total_parts_combined_process.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)#

combined$p_avg[combined$Line=="3DA.C.1"] <- NA
combined$c_avg[combined$Line=="2DA.HS.2"] <- NA
combined$g_avg[combined$Line=="2FA.HS.2"] <- NA

write.table(combined, "../processed_data/total_parts_olier_rem.txt", sep="\t")#USE THIS

```

