---
title: "StdDev&outlier_ID"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(cowplot)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(plyr)
library(forcats)
setwd("C:/Users/Anna/Dropbox/AMP_EGK/Projects/Selection/scripts")

combined<-read.table("../processed_data/combined_processed.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

see_pairs<-combined %>% group_by(Well.ID) %>% tally()
see_numbers<-combined %>% group_by(Well.ID, plate) %>% tally()

wmore2<-subset(see_numbers, n>2, select=c(Well.ID,n, plate)) #lines that have more than 2 replicates

wTwo<-subset(see_numbers, n==2, select=c(Well.ID,n,plate)) #lines that have 2 replicates
linesis1<-subset(see_numbers, n==1, select=c(Well.ID,n)) #There are no lines that have 1 replicate
combined$Well.ID[combined$Well.ID=="1DA.DR.D2"] <- "1DA.DR.B2"

```
whol_set<-left_join(see_numbers, combined, by="Well.ID")

prot<-read.table("../processed_data/prot_processed.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot$Well.ID[prot$Well.ID=="1DA.DR.D2"] <- "1DA.DR.B2"
#p_avg<- dplyr::summarize(group_by(prot,Well.ID),p_avg=mean(p_perfly, na.rm=TRUE))#
#newdat<-merge(p_avg, combined, by="Well.ID")

```{r}
combined$Well.ID[combined$Well.ID=="1DA.DR.D2"] <- "1DA.DR.B2"

#average technical replicates
p_avg<- dplyr::summarize(group_by(combined,Well.ID, plate),p_avg=mean(p_perfly, na.rm = TRUE))#
see_numbers[duplicated(see_numbers$Well.ID),]


test<-p_avg %>% separate(Well.ID, c("Box", "Treat", "TissueRep"))
test$Rep<-as.numeric(gsub("[^[:digit:]]", "", test$TissueRep))#Make RIL column
test$Tissue<-gsub("[[:digit:]]","",test$TissueRep)#Make Treatment column
unique(test$Rep)
unique(test$Tissue)

test$Line <- paste(test$Box,test$Treat,test$Rep,sep='.')

write.table(combined_dissected_p, "../processed_data/combined_dissected_p.txt", sep="\t")#USE THIS

p_tot<- dplyr::summarize(group_by(test,Line),p_tot_perfly=sum(p_avg, na.rm = TRUE))#
```


```{r}
combined<-read.table("../processed_data/combined_processed.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
combined$Well.ID[combined$Well.ID=="1DA.DR.D2"] <- "1DA.DR.B2"

see_pairs<-combined %>% group_by(Well.ID) %>% tally()
see_numbers<-combined %>% group_by(Well.ID, plate) %>% tally()

g_avg<- dplyr::summarize(group_by(combined,Well.ID, plate),g_avg=mean(g_perfly, na.rm = TRUE))#
#newdat<-merge(p_avg, combined, by="Well.ID")
see_numbers[duplicated(see_numbers$Well.ID),]

test<-g_avg %>% separate(Well.ID, c("Box", "Treat", "TissueRep"))
test$Rep<-as.numeric(gsub("[^[:digit:]]", "", test$TissueRep))#Make RIL column
test$Tissue<-gsub("[[:digit:]]","",test$TissueRep)#Make Treatment column
unique(test$Rep)
unique(test$Tissue)

test$Line <- paste(test$Box,test$Treat,test$Rep,sep='.')
write.table(test, "../processed_data/combined_dissected_g.txt", sep="\t")#USE THIS


g_tot<- dplyr::summarize(group_by(test,Line),g_tot_perfly=sum(g_avg, na.rm = TRUE))#
```

```{r}
combined<-read.table("../processed_data/combined_processed.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
combined$Well.ID[combined$Well.ID=="1DA.DR.D2"] <- "1DA.DR.B2"

see_pairs<-combined %>% group_by(Well.ID) %>% tally()
see_numbers<-combined %>% group_by(Well.ID, plate) %>% tally()

c_avg<- dplyr::summarize(group_by(combined,Well.ID, plate),c_avg=mean(c_perfly, na.rm = TRUE))#
#newdat<-merge(p_avg, combined, by="Well.ID")
see_numbers[duplicated(see_numbers$Well.ID),]

test<-c_avg %>% separate(Well.ID, c("Box", "Treat", "TissueRep"))
test$Rep<-as.numeric(gsub("[^[:digit:]]", "", test$TissueRep))#Make RIL column
test$Tissue<-gsub("[[:digit:]]","",test$TissueRep)#Make Treatment column
unique(test$Rep)
unique(test$Tissue)

test$Line <- paste(test$Box,test$Treat,test$Rep,sep='.')
write.table(test, "../processed_data/combined_dissected_c.txt", sep="\t")#USE THIS


c_tot<- dplyr::summarize(group_by(test,Line),c_tot_perfly=sum(c_avg, na.rm = TRUE))#
```

```{r}
combined<-read.table("../processed_data/combined_processed.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
combined$Well.ID[combined$Well.ID=="1DA.DR.D2"] <- "1DA.DR.B2"

see_pairs<-combined %>% group_by(Well.ID) %>% tally()
see_numbers<-combined %>% group_by(Well.ID, plate) %>% tally()

l_avg<- dplyr::summarize(group_by(combined,Well.ID, plate),l_avg=mean(l_perfly, na.rm = TRUE))#
#newdat<-merge(p_avg, combined, by="Well.ID")
see_numbers[duplicated(see_numbers$Well.ID),]

test<-l_avg %>% separate(Well.ID, c("Box", "Treat", "TissueRep"))
test$Rep<-as.numeric(gsub("[^[:digit:]]", "", test$TissueRep))#Make RIL column
test$Tissue<-gsub("[[:digit:]]","",test$TissueRep)#Make Treatment column
unique(test$Rep)
unique(test$Tissue)

test$Line <- paste(test$Box,test$Treat,test$Rep,sep='.')
write.table(test, "../processed_data/combined_dissected_l.txt", sep="\t")#USE THIS


l_tot<- dplyr::summarize(group_by(test,Line),l_tot_perfly=sum(l_avg, na.rm = TRUE))#
```

```{r}
whole_body_pg<-merge(p_tot, g_tot, by="Line")
whole_body_cl<-merge(c_tot, l_tot, by="Line")
whole_body<-merge(whole_body_cl, whole_body_pg, by="Line")
write.table(whole_body, "../processed_data/whole_body_combined_process.txt", sep="\t")
```

```{r}
lip_disc<-read.table("../processed_data/combined_dissected_l.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
prot_disc<-read.table("../processed_data/combined_dissected_p.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
gly_disc<-read.table("../processed_data/combined_dissected_g.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
carb_disc<-read.table("../processed_data/combined_dissected_c.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)

parts_body_pg<-merge(prot_disc, gly_disc, by=c("Line", "plate", "Box", "Treat", "Rep", "Tissue", "TissueRep"))
parts_body_cl<-merge(carb_disc, lip_disc, by=c("Line", "plate", "Box", "Treat", "Rep", "Tissue", "TissueRep"))
total_parts<- merge(parts_body_cl, parts_body_pg, by=c("Line", "plate", "Box", "Treat", "Rep", "Tissue", "TissueRep"))

write.table(total_parts, "../processed_data/total_parts_combined_process.txt", sep="\t")

```


lip<-read.table("../processed_data/lip_processed.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)
test<-combined %>% group_by(Well.ID) %>% tally()

## standard deviations. 
```{r}
combined<-read.table("../processed_data/whole_body_combined_process.txt",sep="\t",header=TRUE,stringsAsFactors=FALSE)


l525<-combined$l_tot_perfly
carbs<-combined$c_tot_perfly
prot<-combined$p_tot_perfly
gly<-combined$g_tot_perfly

l525sd<-sd(l525, na.rm=TRUE)# 2.829545
b<-mean(l525, na.rm=TRUE) #7.584354
(l525sd*3)#8.488636
l525olier<-(l525sd*3)  + b #16.07299
l525olier #(highest value within dataset is 14.5)

csd<-sd(carbs, na.rm=TRUE)#0.03081358
csd
c<-mean(carbs, na.rm=TRUE)#.04586591
c
(csd*3 )#0.0924
colier<- (csd*3 ) + c
colier #0.1383066

psd<-sd(prot,na.rm=TRUE)#0.001292078
psd
d<-mean(prot,na.rm=TRUE)#0.003632775
d
(psd*3) #0.003876235
polier<-(psd*3) + d
polier #0.00750901

gsd<-sd(gly, na.rm=TRUE)#0.2362665
gsd
e<-mean(gly, na.rm=TRUE) # 0.4390386
e
(gsd*3) #0.7087996
golier<-(gsd*3) + e 
golier#1.147838
```


#Plots to look for outliers. Really, just plotted data.
```{r}
hist(combined$l_tot_perfly) #??before 0??
hist(combined$c_tot_perfly)
hist(combined$p_tot_perfly)
hist(combined$g_tot_perfly)

liplist<-combined[which((combined$l_tot_perfly> l525olier)),] #0
carblist<-combined[which((combined$c_tot_perfly> colier)),] #1
protlist<-combined[which((combined$p_tot_perfly> polier)),] #1
glylist<-combined[which((combined$g_tot_perfly> golier)),]#1

write.table(carblist, "../processed_data/carblist_outliers.txt", sep="\t")
write.table(liplist, "../processed_data/liplist_outliers.txt", sep="\t")
write.table(protlist, "../processed_data/protlist_outliers.txt", sep="\t")
write.table(glylist, "../processed_data/glylist_outliers.txt", sep="\t")
```


